Understanding Bicycle Theft in High-Risk Neighborhoods: Key Predictors for Targeted Risk Assessment

### 2024-12-01 paper/paper.qmd
edits on data section and reference updated

The cleaned dataset was saved as a Parquet file, chosen for its efficient storage and compatibility with downstream modeling and visualization workflows. This format allowed for fast read-write operations and seamless integration with analysis tools. The cleaning and preparation steps ensured that the dataset was robust and aligned with the study’s goal of identifying theft patterns and predictors in high-risk neighborhoods.Packages used in this paper are 'tidyverse' [@tidyverse], 'here' [@here],'arrow' [@arrow], 'lubridate'[@lubridate], 'testthat' [@testthat], 'rstanarm' [@rstanarm], 'knitr' [@knitr], and 'forcats' [@forcats].

>>>>

The cleaned dataset was saved as a Parquet file, chosen for its efficient storage and compatibility with downstream modeling and visualization workflows. This format allowed for fast read-write operations and seamless integration with analysis tools. The cleaning and preparation steps ensured that the dataset was robust and aligned with the study’s goal of identifying theft patterns and predictors in high-risk neighborhoods.Packages used in this paper are 'tidyverse' [@tidyverse], 'here' [@here],'arrow' [@arrow], 'lubridate'[@lubridate], 'testthat' [@testthat], 'rstanarm' [@rstanarm],'sf'[@sf], 'knitr' [@knitr], and 'forcats' [@forcats].
